---
title: "Lab 11 Student Problem"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```


## Student Problem 01

We are going to walk through the process of fitting a polynomial predictive model to a data set using cross-validation.

(1) Load the `poly_example.csv` data set into your environment and take a look. Plot the data to get an idea of the feature-outcome relationship.

```{r}



```

(2) Create a training and testing data set. The train/test split should be 80/20.

```{r}




```

(3) Write a function that will fit a polynomial model to the data. The function should take a dataframe input and an argument indicating the degree of the polynomial to fit.

```{r}



```

(4) Fit polynomial models from degree 1 to 20 to the entire training dataset. 

```{r}



```

(5) Write a function that will plot predictions from a fit polynomial model to a dataset.

```{r}

## Take a look at broom::augment()



```

(6) Create a faceted plot of all 20 model predictions on the entire training dataset. Save it as a .png file so you can view and share it easily.

```{r}



```

(7) Based on the graph from (6), is it possible to determine which degree fits best?

```{r}



```

(8) Using the code below, perform 10-fold CV to obtain cross-validated RMSE measures to help make your decision for the best degree model to fit. 

```{r}

## Create folds for cross-validation
create_folds <- function(df, k){
  df_k <- df %>%
    slice_sample(prop = 1) %>%
    mutate(fold = 1 + (row_number()-1) %/% (nrow(df)/k))
  return(df_k)
}

## Function to get RMSE
## make sure you have caret installed for calculating RMSE
# install.packages("caret")

get_RMSE <- function(df, model){
  predicted_df <- augment(model, newdata = df) %>%
    select(feature, outcome, .fitted)
  rmse <- RMSE(predicted_df %>% pull(.fitted), predicted_df %>% pull(outcome))
  return(rmse)
}

# Fit model on all but one fold, test on last fold

fit_and_assess <- function(df, f, degree){
  holdout <- df %>%
    filter(fold == f)
  train <- df %>%
    filter(fold != f)
  train_mod <- fit_poly(df = train, degree = degree)
  holdout_rmse <- get_RMSE(df = holdout, model = train_mod)
  return(holdout_rmse)
}

# k-fold cross-validation

perform_k_fold_cv <- function(df, k, degree){
  folded_df <- create_folds(df = df, k = k)
  holdout_rmse_vals <- map_dbl(1:k, function(x) fit_and_assess(df = folded_df, 
                                                               f = x, 
                                                               degree = degree))
  mean_rmse <- mean(holdout_rmse_vals)
  return(mean_rmse)
}


# Perform the same action over varying degrees of polynomials (from 1 to 20)


```

(9) Fit your final model to the whole training set, graph the predictions for the the test set, and report the RMSE for the test set.

```{r}





```
